О множествах точек на плоскости с целочисленными расстояниями

### 2019-05-30 pps-linear-bound/pps-linear-lower-bound.tex
Remove TODO note that has already been done
Implement a TODO note partially

In the present paper we improve Solymosi's results:
firstly, we obtain a greater constant $c$ in Theorem (TODO: the number of theorem and the exact constant),
using the combined approach with the Point Packing in a Square problem;
then, we prove that $l(m,n)=1$ for all possible $m$ and $n$.

@@

TODO: $|\cdot|$ for length, $\#$ for cardinality?

>>>>

In the present paper we improve Solymosi's results:
firstly, we obtain a greater constant $c$ (TODO: the exact constant) in Theorem~\ref{thm:main_estimate},
using the combined approach with the Point Packing in a Square problem;
then, we prove that $l(m,n)=1$ for all possible $m$ and $n$.

@@
